Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-16 manuscript-figures.Rmd
increase resolution of sensitivity analysis

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>% 
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>% 
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = label_wrap_gen(width = 10),
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.ddTR0.rel.sens <- ddTR0.HPD %>%
  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>% 
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>% 
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = label_wrap_gen(width = 10),
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.Topt.rel.sens <- Topt.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  # scale_y_continuous(
  #   limits = c(0,1)
  # ) +
  facet_wrap(~system_label, scales = "free") +
  theme_minimal_hgrid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(1, "lines")
  )
shift_legend(plot.Topt.rel.sens)
```

@@

plot.CTmin.rel.sens <- CT.HPD %>%
  filter(variable == "CTmin") %>%
  filter(sigmaH %in% c(100, Inf)) %>% 
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
  ) +
  facet_grid(cols = vars(system_label),
             rows = vars(sigmaH),
             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
                                                      default = label_parsed)),
             scales = "free") +
  theme_minimal_hgrid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(1, "lines")
  )
plot.CTmin.rel.sens
```

@@

plot.CTmax.rel.sens <- CT.HPD %>%
  filter(variable == "CTmax") %>%
  filter(sigmaH %in% c(100, Inf)) %>% 
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
  ) +
  facet_grid(cols = vars(system_label),
             rows = vars(sigmaH),
             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
                                                      default = label_parsed)),
             scales = "free") +
  theme_minimal_hgrid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(1, "lines")
  )
plot.CTmax.rel.sens
```

@@

plot.CTwidth.rel.sens <- CT.HPD %>%
  filter(variable == "CTwidth") %>%
  filter(sigmaH %in% c(100, Inf)) %>% 
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitiviWty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
  ) +
  facet_grid(cols = vars(system_label),
             rows = vars(sigmaH),
             labeller = labeller(sigmaH = as_labeller(appender_sigmaH,
                                                      default = label_parsed)),
             scales = "free") +
  theme_minimal_hgrid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(1, "lines")
  )
plot.CTwidth.rel.sens
```

>>>>

sens_labels <- as_labeller(c(
        "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
      "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
      "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand DENV",
      "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
      "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
))

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.ddTR0.rel.sens <- ddTR0.HPD %>%
  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $ddTR_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.Topt.rel.sens <- Topt.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  # scale_y_continuous(
  #   limits = c(0,1)
  # ) +
  facet_wrap(~system_label, scales = "free") +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

@@

CTmin_df <- CT.HPD %>%
  filter(variable == "CTmin") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) #%>%

  # Make a stacked plot, colored by parameter
plot.CTmin.rel.sens <- CTmin_df %>% 
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmin.rel.sens
```

@@

plot.CTmax.rel.sens <- CT.HPD %>%
  filter(variable == "CTmax") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmax.rel.sens
```

@@

plot.CTwidth.rel.sens <- CT.HPD %>%
  filter(variable == "CTwidth") %>%
  filter(sigmaH %in% c(10, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitiviWty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTwidth.rel.sens
```
